Incentivizing Exploration with Unbiased History

### 2018-11-01 2level.tex
sketch?
Minor edits.

\begin{proof}[Proof Sketch]
\ascomment{Jieming, pls add a brief proof sketch if you can.}
\end{proof}

@@

To simplify presentation of the proofs, we will make the following assumption.%
\footnote{This assumption can be removed, without any conceptual difficulty, but at the cost of a somewhat lengthier proofs.}

>>>>

\begin{proof}[Proof Sketch]
\ascomment{Jieming, pls add a brief proof sketch if you can.}
\jmcomment{The main idea of the proof is to consider the case when all pulled arms have bad realized rewards (i.e. 0). }
\jmcomment{Actually, not clear about how to write a sketch for a proof of 8 lines.}
\end{proof}

@@

The proofs can be found in Appendix~\ref{app:warmup}. To simplify presentation, here and elsewhere we make the following assumption (which can be removed at the cost of a somewhat lengthier proofs).
